Tropical Andes IUCN Montane and Lowland forest

### 2023-07-31 code/L0/L0_TropicalAndes_IUCNhabitatClassification.Rmd
convert to spatRaster, spatVector, and sf write output to file

# Load required packages
```{r}
library(raster)
library(sf)
library(rnaturalearth)
library(dplyr)
```

@@

# Subset world map. In this case we are removing the Galapagos by defining the bounding box around the Ecuador polygon.
study_region <-  worldMap %>% filter(sovereignt == "Bolivia" | sovereignt == "Ecuador" | sovereignt == "Venezuela" | sovereignt == "Colombia" | sovereignt == "Peru")
plot(study_region$geometry)
```

@@

>>>>

# Load required packages
```{r}
library(raster)
library(sf)
library(rnaturalearth)
library(dplyr)
library(terra)
```

@@

# Subset world map to Tropical Andes
study_region <-  worldMap %>% filter(sovereignt == "Bolivia" | sovereignt == "Ecuador" | sovereignt == "Venezuela" | sovereignt == "Colombia" | sovereignt == "Peru")
plot(study_region$geometry)
```

@@

# Convert to sf
```{r}
# convert to SpatRaster
TA_iucn_habitat_forest_sr <- as(TA_iucn_habitat_forest, "SpatRaster")
TA_iucn_habitat_forest_sr
```

```{r}
TA_iucn_habitat_forest_sv <- as.polygons(TA_iucn_habitat_forest_sr)
TA_iucn_habitat_forest_sv
plot(TA_iucn_habitat_forest_sv)
```

```{r}
TA_iucn_habitat_forest_shape <- sf::st_as_sf(TA_iucn_habitat_forest_sv)
TA_iucn_habitat_forest_shape
plot(TA_iucn_habitat_forest_shape)
```

# Save shapefile
```{r}
st_write(TA_iucn_habitat_forest_shape, file.path(output_path, "TropicalAndes_IUCNHabitat_Forest.shp"), overwrite=TRUE)
```
